\documentclass{resume}

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Christopher J. Buresch} 
\address{Preferred Name: Cj \\ he/him \\ Senior Software Engineer \\ Seattle, WA} 
\address{\href{mailto:contact@csubj.io}{contact@csubj.io} \\ \href{https://www.linkedin.com/in/csubj}{linkedin/csubj} \\ \href{https://github.com/csubj}{gh/csubj} \\  \href{https://csubj.io}{csubj.io}} 

\begin{document}

%----------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}
Seeking a team focusing on big data problems! I enjoy and specialize in massively distributed, highly available, and fault-tolerant services; working on everything from the metal (or cloud) up.
\end{rSection}

%----------------------------------------------------------------------------
% TECHNICAL STRENGTHS	
%----------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Proficient Languages & Scala, Java, Python, C\#, SQL \\
Relevant Experience with & Scalding / MapReduce, Airflow, Hadoop, Docker, K8s  \\
Learning Languages & Rust, Go \\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Senior Software Engineer} \hfill Sept 2022 - Nov 2022\\
Blobstore (Distributed Storage), Twitter, Inc. \hfill \textit{Seattle, WA}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Designed and implemented a new chargeback model and service to give customers more granular and accurate resource charges for their use-case. Charges are per dataset by data locality, storage tier, class, and resource.
     \item Wrote a new compliance service that might edit access to or delete out-of-compliance datasets when signaled from the InfoSec or Legal team.
     \item Maintained anti-data-entropy services and tooling, processed massive metadata datasets in multi-step pipelines to ensure customer dataset integrity.
     \item Responsible for service design and code, monitoring, tooling, system health, system config, load testing, capacity planning and oncall.
 \end{itemize}

 \textbf{ Site Reliability Engineer II --- Software Engineer II} \hfill Dec 2018 - Sept 2022 \\
Blobstore (Distributed Storage), Twitter, Inc. \hfill \textit{Seattle, WA}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Designed and built a topology-aware locking service to ensure automation and deploys could operate in parallel without affecting service health. This unlocked other opportunities like automated deployments, which increased release cadence from monthly to weekly.
     \item Wrote compliance automation using Airflow for kernel and firmware updates. Rolls 8k machines across multiple datacenters in less than 30 days with no manual intervention and limited service impact. 
     \item Migrated multiple services from baremetal to Aurora (Mesos) compute clusters to ease operational burden and to improve development velocity.
     \item Responsible for service monitoring and tooling, system health, system config, load testing, capacity planning and oncall.
 \end{itemize}

\textbf{Software Engineer} \hfill Aug 2015 - Nov 2018\\
Dynamics, Microsoft Corporation \hfill \textit{Seattle, WA}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Started in SRE moved to SWE for more responsibilities and larger breadth of work. Supported product services, service infrastructure on Azure and service health. 
 \end{itemize}
\end{rSection} 

%----------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------

\begin{rSection}{Education}
    \textbf{Bachelor of Science, Computer Science} \hfill 2011 - 2015 \\ Gonzaga University  \hfill \textit{Spokane, WA} \\ \\
    {\bf Clubs and Activities} \\
    \begin{tabular}{ @{} l @{\hspace{6ex}} l }
    Men's Rowing, Div. 1 \> \textit{2011-12} & ACM ICPC, PNW \> \textit{2012, \textquotesingle13, \textquotesingle14} \\
    Computer Science Club \> \textit{2012-15} & Math Club \> \textit{2013-15} \\
    Cycling Club \> \textit{2013-15} & WSU Hackathon \> \textit{2015} \\
\end{tabular}\\

    \begin{tabbing}
        \hspace{4cm} \= \hspace{5cm} \= \kill 
        {\bf Achievements} \\
        3rd On-Site, ACM ICPC (PNW) \textit{2013}, \textit{2014} \\
        \end{tabbing}
\end{rSection}
%----------------------------------------------------------------------------
\begin{rSection}{Leadership} 
    \begin{itemize}
        \item Mentored 3 new graduate hires and interns. Held bi-weekly or weekly 1:1's to help them ramp up into Twitter Engineering.
        \item Ambassador for Twitter Seattle 2021-2022. Responsible for planning holiday events, creating opportunities for colleagues to socialize, assisting onsite operations management.
    \end{itemize}
\end{rSection}
%----------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular Activities} 
    \begin{itemize}
        \item Avid Mountain Climber! Summited Mt. Baker, Mt. Shuksan, and Mt. Hood. 
        \item Avid 3d Printer enthusiast! I model and print practical, or not-so-practical, objects. If you can think it, you can print it!
    \end{itemize}
\end{rSection}
\end{document}

