\begin{mdframed}[linewidth=2,linecolor=blue, innertopmargin=1em, innerbottommargin=1em, topline=false, rightline=false, bottomline=false]
    \textbf{Senior Software Engineer} \hfill Dec 2018 - Nov 2022\\
    Twitter, Inc. - Blobstore (Distributed KV Object Storage)\hfill \textit{Seattle, WA}

    As a team of nine, we managed over 70PB of user data, handling 100 million requests per day in an on-premises, multi-datacenter, eventually consistent distributed system developed in-house. As the infrastructure lead, I oversaw approximately 8,000 physical machines, managed compliance and chargeback reporting, hardware provisioning and automation, observability, tooling, deployments, anti-entropy services, and delivered critical service features.
    
    {\bf Accomplishments}
     \begin{itemize}
        \itemsep -5pt {} 
         \item Developed and automated chargeback reporting for customer data, transforming a manual and annual process into a daily automated metric covering network, API usage, storage class, and data locality charges. 
         \begin{itemize}
            \item Customers could now make informed decisions and assess how service changes impact cost.
            \item Helped the team prioritize features to help teams improve performance and cut costs like allowing customers to choose replica count per dataset or which datacenter to write to. 
         \end{itemize}
         \item Developed a state-aware locking service that would approve operations on the dataset allowing operators to work safely and independently without impacting service health or causing downtime. 
         \begin{itemize}
            \item This enabled no-touch deployments and hardware failure remediation, saving weeks of developer operational toil annually.
            \item Oncall pages reduced from 90/wk to 4-5/wk
            \item Deployment frequency increased from several times a quarter to weekly for stateful services and twice a week for stateless.
         \end{itemize}
         \item Compliance automation rolled 8k hosts in less than 25 days with no manual intervention and negligible service impact. As a result Blobstore was consistently in the top 5 of patched fleets across the company. 
         \item Implemented anti-entropy services to scan large metadata dumps, billions of keys processed via MapReduce fed a key-list to repair workers to patch production datasets every week. 
         \item Migrated stateless services from baremetal to Aurora Mesos compute to ease operational burden, improve developer velocity and service reliability as well as cut \$100k from annual COGS.
     \end{itemize}
    \end{mdframed}
